%-----------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------

\documentclass{resume}

\usepackage{bookmark}
\usepackage{paralist}
\usepackage{multirow}

% Modify document margins
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue
}

\usepackage[backend=bibtex]{biblatex}
\addbibresource{bib/resume.bib}
\addbibresource{bib/proceedings.bib}

%-----------------------
%   HEADER SECTION
%-----------------------

\name{Georgios ``George'' Balatsouras}
\address{23 Achaion Street \\ Agia Paraskevi (Athens 15343), Attica, Greece}
\address{(Home) +30 210 6004683 \\ (Cell) +30 6944 205788 \\
  \href{mailto:gbalats@gmail.com}{\nolinkurl{gbalats@gmail.com}}}

\begin{document}
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}

%------------------------------
%     EDUCATION SECTION
%------------------------------

\begin{rSection}{Education}

{\bf Ph.D. Candidate,} Static Program Analysis \hfill {2012 --} \\
Ethnikon kai Kapodistriakon Panepistimion Athinon / University of Athens \\
Department of Informatics \& Telecommunications \\
Advisor: Assoc.~Prof.~Yannis Smaragdakis
(\href{mailto:smaragd@di.uoa.gr}{\nolinkurl{smaragd@di.uoa.gr}})

{\bf Master of Science,} Computing Systems \hfill {2009 -- 2012} \\
Ethnikon kai Kapodistriakon Panepistimion Athinon / University of Athens \\
Department of Informatics \& Telecommunications \\
Grade: $9.78 / 10$. Top of graduating class (31 graduates).

{\bf Bachelor of Science,} Computer Science \hfill {2004 -- 2009}  \\
Ethnikon kai Kapodistriakon Panepistimion Athinon / University of Athens \\
Department of Informatics \& Telecommunications \\
Grade: $8.80 / 10$. Top of graduating class (\mytilde{}50 graduates).

\end{rSection}

%------------------------------
%   WORK EXPERIENCE SECTION
%------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{LogicBlox, Inc}
  {April 2012 -- August 2012}
  {Software Engineer Intern, Compiler Technologies}
  {Atlanta, GA, USA}
\item Supervisor: Shan Shan Huang
  (\href{mailto:ssh@logicblox.com}{\nolinkurl{ssh@logicblox.com}})
\itemsep +0.5pt % increase space between items
\item Contributed to the active development of \textsc{BloxAnalysis},
  a tool used to perform static analysis of Datalog programs
  by representing them in a LogicBlox workspace.
\item Implemented a clone-detection library using \textsc{BloxAnalysis}
  that is able to
  \begin{inparaenum}[(i)]
  \item trace isomorphic formulas,
  \item identify redundant rules in Datalog programs, and
  \item detect alternate indices that can be used in place of original
    predicates for optimization purposes.
  \end{inparaenum}
\item Implemented a string-concatenation library that reduces the
  space complexity of the intermediate materialized strings from
  $O(n^2)$ to $O(nlogn)$.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}
  {University of Athens}
  {July 2011 -- present}
  {Research Assistant, Dept. of Informatics \& Telecommunications}
  {Athens, Greece}
\item Supervisor: Assoc. Prof. Yannis Smaragdakis
  (\href{mailto:smaragd@di.uoa.gr}{\nolinkurl{smaragd@di.uoa.gr}})
\item Project: PADECL (``Advanced Program Analysis Using Declarative
  Languages'')
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}
  {University of Athens}
  {October 2010 -- June 2011}
  {Research Developer, Dept. of Informatics \& Telecommunications}
  {Athens, Greece}
\item Supervisor: Prof. Alex Delis
  (\href{mailto:ad@di.uoa.gr}{\nolinkurl{ad@di.uoa.gr}})
\item Project: \href{http://pernasvip.di.uoa.gr/index.php}{PERNASVIP}
\item Description: Development of the Itinerary Planner Server,
  i.e. the server who generates the
  \href{http://pernasvip.di.uoa.gr/index.php/gen-spef/itinerary-example}{itineraries}
  that will be used for navigation by the end-users of the system
\end{rSubsection}

\end{rSection}

\begin{rSection}{Languages and Certificates}
  Greek (native), English (fluent) \\
  Certificate of Proficiency in English, University of Michigan (USA)
  \hfill 2003
\end{rSection}


%----------------------------------
%   TECHNICAL STRENGTHS SECTION
%----------------------------------

\begin{rSection}{Technical Skills}

{\renewcommand{\arraystretch}{1.3}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }

Programming Languages
   & C/C++, Java, Python, Bash, Haskell, Prolog, Datalog \\

Version Control Systems
   & Git, Mercurial, Subversion \\

Editors and IDEs
   & Emacs, Eclipse, NetBeans, Microsoft Visual Studio 6 \\

Build Automation
   & GNU Make, Apache Ant, Apache Maven \\

UNIX Skills
   & Shell Scripting, Systems Programming, Command-line Utilities \\

Databases and Tools
   & SQL, MySQL, JDBC, DBDesigner \\

Compilers and Debuggers
   & GCC / G++, GDB, Valgrind \\

Concurrent Programming
   & Pthreads, MPI, Java (low-level API, \texttt{java.util.concurrent.*}) \\

Operating Systems
   & Linux, BSD, Unix and Unix-like operating systems, Windows \\

Frameworks
   & ASM, BCEL, AspectJ, CGAL, ECLiPSe \\

Web Development
   & HTML5 + CSS, PHP, JSP \\

Other
   & GNU Bison + Flex Lexical Analyzer, \LaTeX{}, LibreOffice \\
\end{tabular}}
\end{rSection}

%-------------------------------------------
%   EXTRA-CURRICULAR ACTIVITIES SECTION
%-------------------------------------------

\begin{rSection}{Activities}
  {\bf Teaching Assistant} \hfill {2009 -- 2014} \\
  University of Athens - Dept. of Informatics \& Telecommunications \\
\end{rSection}

\begin{rSection}{Extra-Curricular Activities}
  Reading, Music (piano, guitar), Soccer \\
\end{rSection}


%---------------------------
%   PUBLICATIONS SECTION
%---------------------------

\begin{rSection}{Publications}
  \begin{rSubsection}{}{}{}{}
    \itemsep +0.5pt % increase space between items
  \item \fullcite{jphantom}
  \item \fullcite{setbased}
  \end{rSubsection}
\end{rSection}

\begin{rSection}{Grants and Awards}
  \begin{rSubsection}{}{}{}{}
  \item SIGPLAN Professional Activities Committee (PAC) travel grant
    for ACM OOPSLA 2013.
  \end{rSubsection}
\end{rSection}

\end{document}
